Part B-2

### 2022-08-09 msca-pf-part-b2.tex
link tables correctly

@@

Please provide an overview list of all participating organisations (the
beneficiary and, where applicable, all associated partners) using template
table 5.1 below, and more detailed information for each of the participating
organisations (using a separate table for each organisation) using template
table 5.2 below.

@@

\subsection{Template table: Overview of Participating Organisations}

@@

\subsection{Template table: Capacity of the Participating Organisations}

>>>>

% NOTE: this needs to be kept so that the sections match the template!
\setcounter{section}{3}

@@

Please provide an overview list of all participating organisations (the
beneficiary and, where applicable, all associated partners) using template
table~\ref{ssc:table1} below, and more detailed information for each of the
participating organisations (using a separate table for each organisation) using
template table~\ref{ssc:table2} below.

@@

\subsection{Template table: Overview of Participating Organisations}
\label{ssc:table1}

@@

\subsection{Template table: Capacity of the Participating Organisations}
\label{ssc:table2}
